Response to Reviewers

### 2021-11-12 Scripts/Initial_Analysis.Rmd
Updates of the top stocks for SSR

test_map <- World_eez_sf %>% 
  left_join(test,
            by = "eezid") %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = emerging_yr
    )
  )+ scale_fill_viridis(
    limits = c(2000,2070),
    breaks = seq(2000,2070,10)#,
    # direction = -1
  ) +
  my_ggtheme_m() +
  ggsave("botTemp_ToE.png",
         width = 12,
         height = 10,
         units = "in"
  )

@@

@@

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  # group_by(sau_fishing_entity,fishing_entity_id,tresh,variable) %>% 
  # summarise(sum_value = sum(value,na.rm=T)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 10 most valuable stocks

@@

  map <- ggplot(World_map_top) +
    geom_sf(
      aes(
        fill = mean #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    # geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    scale_fill_viridis("Average year of range shift",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       direction = -1
    ) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(legend.key.width = unit(5, "line")) +

    guides(
      fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

@@

##### New Fig. 4. Top shifting stocks/EEZs weighted (proportion)

```{r, top_stocks_eez, eval = F, echo = F}

Value_map_data %>% 
  group_by(variable,tresh) %>% 
  top_frac(0.10,participation) %>% 
  filter(tresh == "tresh_two",
         variable == "value") %>% 
  # View()
  left_join(Sau_data) %>% 
  group_by(variable,tresh) %>% 
  top_frac(0.10,value) %>%
  left_join(my_path("G","SAU","exploited_species_list.csv",read = T)) %>% 
  ggplot() +
  geom_bar(
    aes(
      x = common_name,
      y = value
    ),
    stat = "identity"
  ) +
  facet_wrap(~sau_fishing_entity,
             scale = "free") +
  theme(axis.text.x = element_text(angle = 90))

@@

  Prop_map <- ggplot() +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
    geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_point(data = subset(Map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
               aes(start_lon,
                   start_lat
               ),
               size = 0.05,
               col = "gray80",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
              aes(X,
                  Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 0.3,
              lineend = "round",
              arrow = arrow(length = unit(0.008, "npc"),
                            ends = "first"),
              show.legend = NA) +
    # Closeup Rectangles 
    # geom_rect(data=Rectangles,
    #           aes(xmin=x1, 
    #               xmax=x2,
    #               ymin=y1,
    #               ymax=y2),
    #           color="grey50", 
    #           fill = NA,
    #           linetype = "dashed"
    # ) +
    my_ggtheme_m() +
    scale_colour_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # option="magma",
      # direction = -1
    ) +
    scale_fill_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # alpha = 0.8
      # option="magma",
      # direction = -1
    ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )

@@

  Lat_am_map <- ggplot() +
    geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_point(data = subset(Lat_am_data, time_step == time & per_plot < 0 ),
               aes(start_lon,
                   start_lat,
                   col = per_plot),
               size = 1,
               col = "gray30",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(Lat_am_paths, time_step == time & per_plot > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
    labs(x = "", y = "") +
    scale_x_continuous(breaks = seq(-100,60,10)) +
    scale_y_continuous(breaks = seq(10,30,10)) +
    my_ggtheme_m() +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$per_plot)),
      breaks = seq(0,max(Lat_am_data$per_plot),10),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$per_plot)),
      breaks = seq(0,max(Lat_am_data$per_plot),10),
      # option="magma",
      # direction = -1
    )

@@

  Eu_map <- ggplot() +
    geom_sf(data = Eu_eez, size = 0.5, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_point(data = subset(Eu_data, time_step == time & per_plot < 0 ),
               aes(start_lon,
                   start_lat,
                   col = per_plot),
               size = 1,
               col = "gray30",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(Eu_paths, time_step == time & per_plot > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-15, 30), ylim = c(45, 65)) +
    labs(x = "", y = "") +
    scale_y_continuous(breaks = seq(45,65,10)) +
    # scale_x_continuous(breaks = seq(45,65,5)) +
    my_ggtheme_m() +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Eu_data$per_plot)),
      breaks = seq(0,max(Eu_data$per_plot),5),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Eu_data$per_plot)),
      breaks = seq(0,max(Eu_data$per_plot),5),
      # option="magma",
      # direction = -1
    )#;Eu_map

@@

@@

  map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    geom_sf(data = World_map_part,
            aes(fill = participation),
            color =  "white",
            size = 0.1
    ) +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    scale_fill_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c(">2100",seq(2075,2000,-25)) # not inluding the > because we
    ) +
    my_ggtheme_m() +
    facet_wrap(~method,
               nrow = 2)

>>>>

test_map <- World_eez_sf %>% 
  left_join(test,
            by = "eezid") %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = emerging_yr
    )
  )+ scale_fill_viridis(
    limits = c(2000,2070),
    breaks = seq(2000,2070,10)#,
    # direction = -1
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  ggsave("botTemp_ToE.png",
         width = 12,
         height = 10,
         units = "in"
  )

@@

SummaryProp(taxon_key)

@@

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  # group_by(sau_fishing_entity,fishing_entity_id,tresh,variable) %>% 
  # summarise(sum_value = sum(value,na.rm=T)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 5 most valuable stocks
  top_n(5,value)

@@

  map <- ggplot(World_map_top) +
    geom_sf(
      aes(
        fill = mean #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    # geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    scale_fill_viridis("Average year of range shift",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       direction = -1
    ) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(legend.key.width = unit(5, "line")) +
    guides(
      fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

@@

@@

  Prop_map <- ggplot() +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
    geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_point(data = subset(Map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
               aes(start_lon,
                   start_lat
               ),
               size = 0.05,
               col = "gray80",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
              aes(X,
                  Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 0.3,
              lineend = "round",
              arrow = arrow(length = unit(0.008, "npc"),
                            ends = "first"),
              show.legend = NA) +
    # Closeup Rectangles 
    # geom_rect(data=Rectangles,
    #           aes(xmin=x1, 
    #               xmax=x2,
    #               ymin=y1,
    #               ymax=y2),
    #           color="grey50", 
    #           fill = NA,
    #           linetype = "dashed"
    # ) +
    my_ggtheme_m(leg_pos = "bottom") +
    scale_colour_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # option="magma",
      # direction = -1
    ) +
    scale_fill_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # alpha = 0.8
      # option="magma",
      # direction = -1
    ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )

@@

  Lat_am_map <- ggplot() +
    geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_point(data = subset(Lat_am_data, time_step == time & per_plot < 0 ),
               aes(start_lon,
                   start_lat,
                   col = per_plot),
               size = 1,
               col = "gray30",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(Lat_am_paths, time_step == time & per_plot > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
    labs(x = "", y = "") +
    scale_x_continuous(breaks = seq(-100,60,10)) +
    scale_y_continuous(breaks = seq(10,30,10)) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$per_plot)),
      breaks = seq(0,max(Lat_am_data$per_plot),10),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$per_plot)),
      breaks = seq(0,max(Lat_am_data$per_plot),10),
      # option="magma",
      # direction = -1
    )

@@

  Eu_map <- ggplot() +
    geom_sf(data = Eu_eez, size = 0.5, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_point(data = subset(Eu_data, time_step == time & per_plot < 0 ),
               aes(start_lon,
                   start_lat,
                   col = per_plot),
               size = 1,
               col = "gray30",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(Eu_paths, time_step == time & per_plot > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-15, 30), ylim = c(45, 65)) +
    labs(x = "", y = "") +
    scale_y_continuous(breaks = seq(45,65,10)) +
    # scale_x_continuous(breaks = seq(45,65,5)) +
    my_ggtheme_m(leg pos = "bottom") +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Eu_data$per_plot)),
      breaks = seq(0,max(Eu_data$per_plot),5),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Eu_data$per_plot)),
      breaks = seq(0,max(Eu_data$per_plot),5),
      # option="magma",
      # direction = -1
    )#;Eu_map

@@

##### Fig. TOP 5

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  # group_by(sau_fishing_entity,fishing_entity_id,tresh,variable) %>% 
  # summarise(sum_value = sum(value,na.rm=T)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 5 most valuable stocks
  top_n(5,value)

top_taxon_list <-  unique(top_stocks_per_country$taxon_key)
# Read proportion results
suppressMessages(
top_prop_results <- PropChange(top_taxon_list, links="y") %>%
  filter(!is.na(eez_neighbour)) %>%
  mutate(per_mid_plot =ifelse(per_mid >= 100, 100,
                              ifelse(per_mid <= -100,-100,per_mid)
  ),
  per_early_plot =ifelse(per_early >= 100, 100,
                         ifelse(per_early <= -100,-100,per_early)
  )
  )
)

# Prepare data from results
top_data <- top_prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
top_network_data_sf <- top_data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  # st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(top_data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  sf::st_sf(crs = 4326)
  # sf::st_sf(crs = "+proj=eck4") # for tbular plot

#  unpack the coordinates of each feature 
coord_data <- as.data.frame( st_coordinates(st_cast(top_network_data_sf,"MULTILINESTRING")$geometry))

c(top_network_data_sf$line_id, top_network_data_sf$coords) %<-% (
  coord_data %>% 
    rename(subline_id = L1) %>%   
    nest(-L2)
)

# Create data path for line connections
top_paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest(cols = c(coords)) %>%
  mutate_at(vars(X,Y), round,2) %>% 
  gather("time_step","per_chng",per_early:per_mid) %>% 
  mutate(per_plot = ifelse(per_chng > 50,50,per_chng),
         direction = ifelse(per_chng > 0,"positive","negative")
         )

# Proportion map data 
top_map_data <- top_data %>% 
  gather("time_step","per_chng",per_early:per_mid) %>% 
  mutate(per_plot = ifelse(per_chng > 50,50,per_chng))

time <- "per_early"

top_rop_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = World_map, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
  geom_point(data = subset(top_map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
             aes(start_lon,
                 start_lat
             ),
             size = 0.05,
             col = "gray80",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(top_paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
            aes(X,
                Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.9,
            lineend = "round",
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_colour_viridis(
    name= "Changes in catch proportion",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
  ) + guides(
      color=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

ggsave(
  plot = top_rop_map,
  filename = "./Figures/top_ssr.png",
  width = 12,
  height = 8,
  units = "in"
)

@@

  map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    geom_sf(data = World_map_part,
            aes(fill = participation),
            color =  "white",
            size = 0.1
    ) +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    scale_fill_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c(">2100",seq(2075,2000,-25)) # not inluding the > because we
    ) +
    my_ggtheme_m(leg_pos = "bottom") +
    facet_wrap(~method,
               nrow = 2)

### 2021-11-12 Scripts/Manuscript.Rmd
Updates of the top stocks for SSR

>>>>

**Having high-valuable stocks shifting sooner could be a much bigger concern than having many low-value stocks shifting. On average, countries will see a range shift of the top 5 most valuable stocks by 2038 $\pm$ 16 years (Figure S-NEW). Moreover, our projections suggest that these high value stocks are already shifting in 66% of coastal nations, with the regions of Polynesia (n = 22), Sub-Saharan Africa (n = 36) and Latin America and the Caribbean (n = 62) presenting the larger number of shifting stocks (20% of total high value stocks).**

### 2021-11-12 Scripts/responses_rev_gcb.Rmd
Updates of the top stocks for SSR

Further, I am concerned about the averaging and weighting of species that is done across species in this analysis. As one example, why is the geographic centroid (used in the calculation of TI) not weighted by probability of occurrence? Fish stocks are not evenly distributed across their entire range, and unweighted centroids can severely skew the actual distribution of the species.

- **Response:** We agree with the reviewer that and unweighted centroid can severely skew the actual distribution of the species and influence our results. We have revised the manuscript to clarify that we did account for the heterogeneous distribution of fish stocks across their entire range. The geographic centroid of each stock is indeed weighted by the abundance of the stock. The DBEM uses the species probability of occurrence to estimate the biomass of the species at each 0.5 x 0.5 gridcell as indicated from lines XX to XX of the methods. The centroid of a transboundary stock was determined by the average latitude and longitude ($lon_{ts}$) of the grid cells holding the specified percentile ($per^{th}$) of the projected transboundary stock abundance (see below). This is, we determined the centroid of the stock using only those regions where abundance was higher (i.e., using the probability of occurrence of the DBEM). Moreover, we estimated the sensitivity of our results to the (arbitrarily) $per^{th} = 95^{th}$ percentile threshold as described in lines XX and shown in Figure S6 of the supplements. It reads as follows in line XX:

@@

- **Response:** This is a very good observation and we believe it has increased the impact of our manuscript. We have included two new figure (**Supplement Figure XX**) showing the average range shift of the top 5 most valuable transboundary stocks per country in addition to the following text on line XX:

  - Line XX: *Having high-valuable stocks shifting sooner could be a much bigger concern than having many low-value stocks shifting. On average, countries will see a range shift of the top 5 most valuable stocks by 2038 $\pm$ 16 years (Figure S-NEW). Moreover, our projections suggest that these high value stocks are already shifting in 66% of coastal nations, with the regions of Polynesia (n = 22), Sub-Saharan Africa (n = 36) and Latin America and the Caribbean (n = 62) presenting the larger number of shifting stocks (20% of total high value stocks).*

@@

We have made the following modifications to the manuscript:

  - Line XX, *We estimated the participation of the transboundary stocks that are shifting between neighboring EEZs relative to the total revenue from all transboundary stocks that each EEZ has. On average, shifting transboundary stocks represented 27% to 23% (1 and 2 s.d. thresholds) of annual revenue from fisheries targeting transboundary stocks across the world's EEZs between 2004 and 2010 (Fig. \@ref(fig:toeFigure2)A).*

@@

- **Response: (Incomplete)** Many thanks for this observation. We have revised the whole manuscript to be sure verb tense is maintained through the document.

@@

- **Response:** This is indeed the definition of our stock. Please refer to our responses to the main comment.

@@

- **Response:** Please see reposes to the reviewer's main comments. We have defined a trnaboundary stock as follows;

>>>>

Further, I am concerned about the averaging and weighting of species that is done across species in this analysis. As one example, why is the geographic centroid (used in the calculation of TI) not weighted by probability of occurrence? Fish stocks are not evenly distributed across their entire range, and un-weighted centroids can severely skew the actual distribution of the species.

- **Response:** We agree with the reviewer that and un-weighted centroid can severely skew the actual distribution of the species and influence our results. We have revised the manuscript to clarify that we did account for the heterogeneous distribution of fish stocks across their entire range. The geographic centroid of each stock is indeed weighted by the abundance of the stock. The DBEM uses the species probability of occurrence to estimate the biomass of the species at each 0.5 x 0.5 gridcell as indicated from lines XX to XX of the methods. The centroid of a transboundary stock was determined by the average latitude and longitude ($lon_{ts}$) of the grid cells holding the specified percentile ($per^{th}$) of the projected transboundary stock abundance (see below). This is, we determined the centroid of the stock using only those regions where abundance was higher (i.e., using the probability of occurrence of the DBEM). Moreover, we estimated the sensitivity of our results to the (arbitrarily) $per^{th} = 95^{th}$ percentile threshold as described in lines XX and shown in Figure S6 of the supplements. It reads as follows in line XX:

@@

- **Response:   (INCOMPLETE)** This is a very good observation and we believe it has increased the impact of our manuscript. We have included two new figures (**Supplement Figures XX and XX**) showing the average range shift and SSR of the top 5 most valuable transboundary stocks per country (Please note that figure 4 has been removed from the revised manuscript).

  - Range shift, line XX: *Having high-valuable stocks shifting sooner could be a much bigger concern than having many low-value stocks shifting. On average, countries will see a range shift of the top 5 most valuable stocks by 2038 $\pm$ 16 years (Figure S-NEW). Moreover, our projections suggest that these high value stocks are already shifting in 66% of coastal nations, with the regions of Polynesia (n = 22), Sub-Saharan Africa (n = 36) and Latin America and the Caribbean (n = 62) presenting the larger number of shifting stocks (20% of total high value stocks).*

@@

- SSR , line XX: **

![Top 5](../Figures/top_ssr.png)

@@

- **Response: (INCOMPLETE)** Many thanks for this observation. We have revised the whole manuscript to be sure verb tense is maintained through the document.

@@

- **Response:** This is indeed the definition of our stock. We do not deferenciate between transboundary and straddling stocks as per defined in Palacios-Abanes *et al.* (2020). Please refer to our responses to the main comment.

@@

- **Response:** Please see responses to the reviewer's main comments. We have defined a transboundary stock as follows;
